### 2018-07-13 doc/plos/text/manuscript.tex
add subsection evaluation

>>>>

\subsection*{Evaluation}

In a given location over a given period of time, we assess the accuracy of a
set of nowcasts by two measures: mean absolute error (MAE) and root mean
squared error (RMSE). With ground truth vector $\vec{x}$, nowcast vector
$\vec{y}$, and elements indexed by week $w$ of $n$, these measures are defined
as:

\begin{align*}
  \text{MAE} &= \frac{1}{n} \sum_{w=1}^n{\left|x_w - y_w\right|} \\
  \text{RMSE} &= \left( \frac{1}{n} \sum_{w=1}^n{\left(x_w - y_w\right)^2} \right)^\frac{1}{2}
\end{align*}
